Accelerating Genetic ANN Training using the CUDA Platform

### 2010-04-18 doc/paper.tex
Slightly change wording in abstract
git-svn-id: http://svn.scesoc.ca/evolution/trunk@77 fee98b4c-d1c3-4d34-9525-a468159e4a48
Add Computation of ANN Output Values and Conclusion
git-svn-id: http://svn.scesoc.ca/evolution/trunk@78 fee98b4c-d1c3-4d34-9525-a468159e4a48

% ############################################################################
% Abstract
% ############################################################################
\begin{abstract}
We present an implementation of genetic algorithm (GA) training of artificial neural networks (ANNs) targeting commodity graphics cards (GPUs). By carefully mapping the problem onto the unique GPU architecture, we achieve order-of-magnitude speedup over a conventional CPU implementation. Furthermore, we show that the speedup is consistent across a wide range of population and training set sizes. This performance boost enables classifier design to span a wider range of population sizes and number of generations affording better classifiers and improved understanding of long-term trends in genetic algorithm convergence. Finally, we apply this method to the design of a classifier for the 2009 UC San Diego Data Mining Contest.
\end{abstract}

@@

@@

% ############################################################################
\section{Conclusion} \label{concl}
% ############################################################################
Filling this with text so that I can see what the document looks like when it is filled with text and to make sure that everything lines up nicely when it is full of text like this

>>>>

% ############################################################################
% Abstract
% ############################################################################
\begin{abstract}
We present an implementation of genetic algorithm (GA) training of artificial neural networks (ANNs) targeting commodity graphics cards (GPUs). By carefully mapping the problem onto the unique GPU architecture, we achieve order-of-magnitude speedup over a conventional CPU implementation. Furthermore, we show that the speedup is consistent across a wide range of population and training set sizes. This performance boost enables classifier design to span a wider range of population sizes and number of generations affording better classifiers and improved understanding of long-term trends in genetic algorithm convergence. Finally, we demonstrate this method in the context of the 2009 UC San Diego Data Mining Contest.
\end{abstract}

@@

% ----------------------------------------------------------------------------
\subsection{Computation of ANN Output Values} \label{implementation}
% ----------------------------------------------------------------------------
ANN output values are computed by reading feature values and applying the appropriate operations represented by the network topology and parameters. Feature data are organized to enable memory read coalescing. This part of the process is particularly well-suited to the CUDA architecture because it has a very high ratio of mathematical operations to memory accesses (160 multiplications, 4 exponentiations and 80 bytes of memory accesses for our ANN topology).

@@

% ############################################################################
\section{Conclusion} \label{concl}
% ############################################################################
We have presented an implementation of GA training of ANN classifiers for the CUDA platform for GPU programming. By carefully designing memory organization, algorithm computational load and memory access patterns, we have obtained a 10-fold speedup compared to a conventional sequential CPU implementation. Additional workaround were necessary for the low amount of fast on-chip GPU memory. Our method scales across population and training set sizes.
